### 2024-02-15 documentation/thesis/thesis_document.tex
.

Measuring the noise in a magnetic field sensor requires a precise
procedure and a special measurement setup. First, the magnetic field
sensor is placed in a quiet environment to minimize external field
interference. The temperature chamber for all noise tests is set to
\emph{20°C}.

@@

\begin{longtable}[]{@{}lll@{}}
\caption{Sensor noise evaluation results
\label{Sensor_noise_evaluation_results.csv}}\tabularnewline
\toprule
Symbol & Unit & TLV493D\tabularnewline
\midrule
\endfirsthead
\toprule
Symbol & Unit & TLV493D\tabularnewline
\midrule
\endhead
\(\mu_{rv}\) & \(\mu\)T &\tabularnewline
\(\mu_{t}\) & \(\mu\)T &\tabularnewline
\(\mu_{nl}\) & \% &\tabularnewline
\(\sigma_{nl}\) & \% &\tabularnewline
\bottomrule
\end{longtable}

@@

Compared to the \emph{MMC5603NJ}, the temperature plot of the
\emph{TLV493D} shows that the internal temperature sensor is very noisy
(maximum of \(\sigma^2_{t}\)=\emph{2\(^{\circ}\)C})and deviates from the
ambient temperature at almost \emph{10\(^{\circ}\)C}. With a further
measurement run with a different temperature setting of
\emph{30\(^{\circ}\)C}, the offset is reduced to only
\emph{4\(^{\circ}\)C} to the set temperature. However, the noise remains
constant. When using an alternative sensor, this behaviour is reflected
and therefore the internal temperature sensor of the \emph{TLV493D}
should not be used for subsequent temperature compensation.

@@

In the raw data plot, as well as its mean value \(\mu_{rv}\) of both
sensors, an offset can also be recognised, which is dependent on the
ambient conditions. For verification, a reference measurement of the
environment was carried out with the calibrated \emph{Voltcraft GM70}
Telsameter. This provides a \emph{real} baseline value of
\(\mu_{rev}\)=-21\(\mu\)T.

\begin{itemize}
\tightlist
\item
  Plot of the raw measurement data, as well as its mean value
  \(\mu_{rv}\)\(\mu\)T using Baselin
\item
  Plot of the temperature curve over the complete measurement series,
  which was recorded with the sensor's internal temperature sensor
\item
  Noise level as a percentage deviation from the baseline
\item
  Histogram of the noise level with marked standard deviation
\end{itemize}

TODO TABELLE EINORDNUNG MITTELUNGEN ALS TABELLE

>>>>

Measuring the noise in a magnetic field sensor requires a precise
procedure and a special measurement setup. First, the magnetic field
sensor is placed in a quiet environment to minimize external field
interference. The temperature chamber for all noise tests is set to
\(\mu_{trev}\)=21.0\(^{\circ}\) and the sensors are placed 24 hours
before the measurement run in the final measurement configuration inside
of the chamber.

@@

The table \ref{Sensor_noise_evaluation_results.csv} lists the measured
values that were extracted from the measurement data of the sensors
\ref{Sensor_noise_evaluation_results_for_TLV493D_and_MMC5603NJ_with_N=2000_samples_and_no_averaging.png}.
These measured values are categorised below.

: Sensor noise evaluation results
\label{Sensor_noise_evaluation_results.csv}

~\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}\\
\hspace*{0.333em}\textbar{}

@@

The temperature stability of the \emph{TLV493D} with a mean value of
20.68\(^{\circ}\)C and a standard deviation of
\(\sigma_{t}\)=0.53\(^{\circ}\)C indicates a consistent trend. This
implies a constant tendency. The close grouping of the measured values
around the mean value indicates good stability. The confidence interval
is expected to be between 20.15\(^{\circ}\)C and 21.21\(^{\circ}\)C,
which indicates a stable and consistent temperature measurement. This
result is more noisy compared to the temperature stability of the
\emph{MMC5603}.

Both sensors provide an offset to the measured chamber temperature
\(\mu_{trev}\).

With an additional measurement run with a different temperature setting
of 30.0\(^{\circ}\)C, the measured temperature deviations and offsets
remains constant.

Thus, the sensor internal temperature sensors of both tested sensors are
suitable to perform an ambient temperature compensation of measured
values and calibration of the sensor. This is considered in section
\emph{Temperature Sensitivity} \ref{temperature-sensitivity}.

@@

In the raw data plot, as well as its mean value \(\mu_{rv}\) of both
sensors, an offset can also be recognised, which is dependent on the
ambient conditions. For verification, a reference measurement of the
environment was carried out with the calibrated \emph{Voltcraft GM70}
Telsameter next to the sensor \gls{ic} This provides a \emph{real}
baseline value of \(\mu_{rev}\)=-21\(\mu\)T.
